### 2022-04-05 chapters/intro/intro.tex
paragraph about physics

>>>>

\modif{The motion of geophysical fluids such as seawater is characterized by the effects of ambient rotation and stratification. The ambient rotation is induced by the Earth's spin and generates the Coriolis forces. Stratification arises from the presence of waters with different temperature and salinity, and therefore different density. Under the action of gravitational forces, heavier waters lower while lighter waters rise, which caused the water column to tend towards a stable stratified equilibrium. However, this equilibrium is disrupted in the presence of discontinuities in horizontal velocities induced by wind and water motion. These baroclinic instabilities generate internal waves, water mixing, and eddies. Eddy activity is especially strong in boundary currents such as the Gulf Stream, where strong horizontal shear occur and where shelf water and deep water masses meet on the shelf break. Capturing such processes require baroclinic models that represent the variations of water density along the water column. However, in regions where the water column is sufficiently homogeneous and shallow that vertical contrasts are negligible, ocean circulation is accurately approximated by barotropic models. Such models use a depth-averaged approach by assuming an homogeneous water column with constant density and are used to model estuaries, coastal regions and shelf seas. Both the baroclinic and the barotropic models usually rely on the hydrostatic equilibrium, \textit{i.e.} vertical accelerations are neglected by assuming that gravity balances the vertical component of the pressure gradient force. Such assumption is only valid when the horizontal scale of the flow is larger than its vertical scale.}
